---
title: "R Notebook"
output: html_notebook
---
Monte Carlo Simulations for "Estimation and Inference in High-Dimensional Panel
Data Models with Interactive Fixed Effects" (2024) by Oliver Linton, 
Maximilian Rücker, Michael Vogt and Christopher Walsh.

```{r}
# hdcce package needs to be downloaded: https://github.com/RueckerM/hdcce
# Load the package "hdcce"
library(hdcce)
```

# Tests
```{r}
# Generate fix parameters
n_dim <- 50
T_dim <- 15
if(T_dim == 15){
  pA_vec <- c(7, 10, 13) # Low Dimensional Setting A 
  pB_vec <- c(31, 151, 301) # Setting B
  pC <- 901 # High-Dimensional Setting C
}else if (T_dim == 50){
  pA_vec <- c(16, 31, 46) # Low Dimensional Setting A 
  pB_vec <- c(91, 451, 901)# Setting B
  pC <- 3001 # High-Dimensional Setting C
}


K <- 3
rho <- 0.25
c_val <- 0.4
```

```{r}
# Folds for cross-validation
n_Folds <- 10
fold_size <- n_dim/n_Folds
fold_vec <- rep(1, fold_size * T_dim)

for (folds in 2:n_Folds) {
  tmp <- rep(folds, fold_size * T_dim) 
  fold_vec <- append(fold_vec, tmp)
}
```




########### Test 1: Check for interceptions and non-conformable data ###########

```{r}
X <- matrix(rnorm(n_dim * T_dim * pA_vec[2]), nrow = n_dim * T_dim, ncol = pA_vec[2])
Y <- rnorm(n_dim*T_dim)
data <- list(x = X, y = Y)

estimation_test <- hdcce_estimator(data, obs_N = n_dim, obs_T = T_dim, 
                                   variant = "Lasso", TRUNC = 0.5, 
                                   foldid = fold_vec, scree_plot = TRUE)

inference_test <- hdcce_inference(data = data, obs_N = n_dim, obs_T = T_dim, 
                                  foldid = fold_vec, COEF_INDEX = 1)
```








######################### Test 2: Simulation exercises #########################
```{r}
library(mvtnorm)
library(tictoc)
```




## Approximation quality 


```{r}
# Initialize parallelization
library(parallel)
library(doParallel)
#source("hdcce_estimator.r")
#source("hdcce_inference.r")
c = detectCores()
N_Sim <- 300
cl = makeCluster(c)
registerDoParallel(cl)

```

```{r}
gamma_vec <- c(1, sqrt(10))
gamma_res <- vector(mode = 'list', length = 2)
p_res_K <- vector(mode = 'list', length = 3)
```

 

```{r}
tictoc::tic()
# If parallelization is not used, replace foreach loop with normal for loop and
# append monte carlo results in a list called "results_Factors" for each simulation run. 
results_Factors = foreach(case = 1:N_Sim) %dopar% {
 count <- 1
for (gamma in gamma_vec) {
 
 for (p in 1:3) {
 # Append data für each i to zero row vector
 XA_tmp <- numeric(pA_vec[p])
 XB_tmp <- numeric(pB_vec[p])
 
 if(p == 3){
  XC_tmp <- numeric(pC)
 }
 
 YA_tmp <-  numeric(1)
 YB_tmp <-  numeric(1)
 
 if(p == 3){
  YC_tmp <-  numeric(1)
 }
 
 YA_INFERENCE_tmp <- numeric(3)
 YB_INFERENCE_tmp <- numeric(3)
 if(p == 3){
  YC_INFERENCE_tmp <- numeric(3)
}
 
 #Group size
 dA <- (pA_vec[p] - 1)/3 
 dB <- (pB_vec[p] - 1)/3
 if(p == 3){
   dC <- (pC - 1)/3
 }
 # Coefficient vector beta
# Corresponds to small T case
 if(T_dim == 15){
 if(p == 1){
   beta_A <- c(c_val, rep(rep(c_val,2),3))
 }
 if(p == 2){
   beta_A <- c(c_val, rep(rep(c_val,3),3))
 }
 if(p == 3){
   beta_A <- c(c_val, rep(c(rep(c_val,3),0),3))
 }
}else{
  betaA_group <- c(rep(c_val, 3), rep(0, dA-3))
  beta_A <- c(c_val, betaA_group, betaA_group, betaA_group)
 }

 
 betaB_group <- c(rep(c_val, 3), rep(0, dB-3))
 beta_B <- c(c_val, betaB_group, betaB_group, betaB_group)

 if(p == 3){
   betaC_group <- c(rep(c_val, 3), rep(0, dC-3))
   beta_C <- c(c_val, betaC_group, betaC_group, betaC_group)
 }
 


 
 
 # Generate factor structure
 F_1 <- as.vector(arima.sim(model = list(ar = 0.5), n = T_dim, 
                          innov = rnorm(n = T_dim, mean = 0, sd = sqrt(0.75))))
 F_2 <- as.vector(arima.sim(model = list(ar = 0.5), n = T_dim, 
                          innov = rnorm(n = T_dim, mean = 0, sd = sqrt(0.75))))
 F_3 <- as.vector(arima.sim(model = list(ar = 0.5), n = T_dim, 
                          innov = rnorm(n = T_dim, mean = 0, sd = sqrt(0.75))))
 
 F_matrix <- cbind(F_1, F_2, F_3)
 
 # Oracle projection matrix
 Pi <- diag(1, T_dim, T_dim) - F_matrix %*% solve((t(F_matrix) %*% F_matrix)) %*% t(F_matrix)
 
 
 # Expectation of component vector G_i ----> We spike the first eigenvalue with value gamma
 muG_A <- c(rep(1, K), rep(gamma,dA), rep(1, 2*dA))
 muG_B <- c(rep(1, K), rep(gamma,dB), rep(1, 2*dB))
 
  if(p == 3){
    muG_C <- c(rep(1, K), rep(gamma,dC), rep(1, 2*dC))
  }

 
 
 SigmaG_A <- matrix(rho, nrow = (K + pA_vec[p] - 1 ), 
                    ncol = (K + pA_vec[p]-1)) + diag(1 - rho, nrow = (K + pA_vec[p] - 1 ), 
                  ncol = (K + pA_vec[p] - 1) )
 SigmaG_B <- matrix(rho, nrow = (K + pB_vec[p] - 1 ), 
                    ncol = (K + pB_vec[p]-1)) +  diag(1 - rho, nrow = ( K + pB_vec[p] - 1 ), 
                  ncol = (K + pB_vec[p] - 1))
 if(p == 3){
   SigmaG_C <- matrix(rho, nrow = (K + pC - 1 ),
                      ncol = (K + pC-1)) + diag(1 - rho, nrow = ( K + pC - 1 ),
                         ncol = (K + pC - 1))
  }


 
 # idiosyncratic error iid across i and t
 eps <- rnorm(n = n_dim * T_dim, mean = 0, sd = 1)
 # nodewise errors iid across i and t
 u <- rnorm(n = n_dim * T_dim, mean = 0, sd = 1) 
 
 
 # idiosyncratic regressor part across i and t
 Z_A <- mvtnorm::rmvnorm(n = n_dim * T_dim, mean = rep(0, (pA_vec[p] - 1), 
                                   sd = diag(1, nrow = (pA_vec[p] - 1), 
                                             ncol = (pA_vec[p] - 1) ))) 
 Z_B <- mvtnorm::rmvnorm(n = n_dim * T_dim, mean = rep(0, (pB_vec[p] - 1), 
                                              sd = diag(1, nrow = (pB_vec[p] - 1), 
                                                   ncol = (pB_vec[p] - 1) )))
 if(p ==3){
   Z_C <- mvtnorm::rmvnorm(n = n_dim * T_dim, mean = rep(0, (pC - 1), 
                                                sd = diag(1, nrow = (pC - 1), 
                                                   ncol = (pC - 1) )))
 }
 
   G_Ai <- mvtnorm::rmvnorm(n_dim , mean = muG_A, sigma = SigmaG_A) # Model components
   G_Bi <- mvtnorm::rmvnorm(n_dim, mean = muG_B, sigma = SigmaG_B)
if(p == 3){
   G_Ci <- mvtnorm::rmvnorm(n_dim, mean = muG_C, sigma = SigmaG_C)
}
 # Empty lists to append the data for each i
 
 for (i in 1:n_dim) {################# Start iteration i #################

   gamma_Ai <- G_Ai[i,1:K]
   gamma_Bi <- G_Bi[i,1:K]
   
   if(p == 3){
    gamma_Ci <- G_Ci[i,1:K]
   }
   
   GammaA_i <- cbind(c(G_Ai[i, (K + 1):(K + dA)], rep(0, 2 * dA)),
                     c(rep(0, dA), G_Ai[i, (K + dA + 1):(K + 2 * dA)], rep(0, dA)),
                     c(rep(0, 2 * dA), G_Ai[i, (K + 2 * dA + 1):(K + 3 * dA)]))
   
   GammaB_i <- cbind(c(G_Bi[i, (K + 1):(K + dB)], rep(0, 2 * dB)),
                     c(rep(0, dB), G_Bi[i, (K + dB + 1):(K + 2 * dB)], rep(0, dB)),
                     c(rep(0, 2 * dB), G_Bi[i, (K + 2 * dB + 1):(K + 3 * dB)]))
   
   if(p == 3){
   GammaC_i <- cbind(c(G_Ci[i, (K + 1):(K + dC)], rep(0, 2 * dC)),
                        c(rep(0, dC), G_Ci[i, (K + dC + 1):(K + 2*dC)], rep(0, dC)),
                        c(rep(0, 2 * dC), G_Ci[i, (K + 2*dC + 1):(K + 3*dC)]))
   }
     
   
   # Regressors generated with factor structure
   XA_i <- F_matrix %*% t(GammaA_i) + Z_A[((i-1) * T_dim + 1) : (i * T_dim),]
   XB_i <- F_matrix %*% t(GammaB_i) + Z_B[((i-1) * T_dim + 1) : (i * T_dim),]
   if(p == 3){
     XC_i <- F_matrix %*% t(GammaC_i) + Z_C[((i-1) * T_dim + 1) : (i * T_dim),]
   }
   
   
   # First regressor generated with nodewise structure
   XA_i1 <- XA_i[, 1] * sqrt(2/3) + u[((i-1) * T_dim + 1) : (i * T_dim)]
   XB_i1 <- XB_i[, 1] * sqrt(2/3) + u[((i-1) * T_dim + 1) : (i * T_dim)]
   if(p == 3){
     XC_i1 <- XC_i[, 1] * sqrt(2/3) + u[((i-1) * T_dim + 1) : (i * T_dim)]
   }
   
   # Collect the design X_i in a first step
   XA_i <- cbind(XA_i1, XA_i)
   XB_i <- cbind(XB_i1, XB_i)
   if(p == 3){
     XC_i <- cbind(XC_i1, XC_i)
   }
   
   # Generate response variable Y  
   YA_i <- XA_i %*% beta_A + F_matrix %*% gamma_Ai + eps[((i-1) * T_dim + 1) : (i * T_dim)]

   YB_i <- XB_i %*% beta_B + F_matrix %*% gamma_Bi + eps[((i-1) * T_dim + 1) : (i * T_dim)]
  if(p == 3){
    YC_i <- XC_i %*% beta_C + F_matrix %*% gamma_Ci + eps[((i-1) * T_dim + 1) : (i * T_dim)]
  }
   # Generate response Y for INFERENCE
   YA_INFERENCE_i <- matrix(nrow = T_dim, ncol = 3)
   YB_INFERENCE_i <- matrix(nrow = T_dim, ncol = 3)
   if(p == 3){
     YC_INFERENCE_i <- matrix(nrow = T_dim, ncol = 3)
   }
   k <- 1
   for (signal in c(0, 0.1, 0.2)) {
     beta_A_INFERENCE <- beta_A
     beta_A_INFERENCE[1] <- signal
     YA_INFERENCE_i[,k] <- XA_i %*% beta_A_INFERENCE + F_matrix %*% gamma_Ai + eps[((i-1) * T_dim + 1) : (i * T_dim)]
     
     beta_B_INFERENCE  <- beta_B
     beta_B_INFERENCE[1] <- signal
     YB_INFERENCE_i[,k] <- XB_i %*% beta_B_INFERENCE + F_matrix %*% gamma_Bi + eps[((i-1) * T_dim + 1) : (i * T_dim)]
     if(p == 3){
        beta_C_INFERENCE <- beta_C
        beta_C_INFERENCE[1] <- signal
        YC_INFERENCE_i[,k] <- XC_i %*% beta_C_INFERENCE + F_matrix %*% gamma_Ci + eps[((i-1) * T_dim + 1) : (i * T_dim)]
     }
     k <- k + 1
   }
   
 
   # Collect the data 
   XA_tmp <- rbind(XA_tmp, XA_i)
   XB_tmp <- rbind(XB_tmp, XB_i)
   if(p == 3){
     XC_tmp <- rbind(XC_tmp, XC_i)
   }
   
   YA_tmp <- rbind(YA_tmp, YA_i)
   YB_tmp <- rbind(YB_tmp, YB_i)
   if(p == 3){
   YC_tmp <- rbind(YC_tmp, YC_i)
   }
   
   YA_INFERENCE_tmp <- rbind(YA_INFERENCE_tmp, YA_INFERENCE_i)
   YB_INFERENCE_tmp <- rbind(YB_INFERENCE_tmp, YB_INFERENCE_i)
   if(p == 3){
     YC_INFERENCE_tmp <- rbind(YC_INFERENCE_tmp, YC_INFERENCE_i)
   }
   
   
 }
   print(p) ################# End iteration i #################
 XA_tmp <- XA_tmp[-1,] # Remove first row
 XB_tmp <- XB_tmp[-1,]
 if(p == 3){
 XC_tmp <- XC_tmp[-1,]
 }
 
 YA_tmp <- YA_tmp[-1]
 YB_tmp <- YB_tmp[-1]
 if(p == 3){
 YC_tmp <- YC_tmp[-1]
 }
 
 YA_INFERENCE_tmp <- YA_INFERENCE_tmp[-1,]
 YB_INFERENCE_tmp <- YB_INFERENCE_tmp[-1,]
 if(p == 3){
   YC_INFERENCE_tmp <- YC_INFERENCE_tmp[-1,]
 }
   

 
   # Oracle Projected Data
  YA_oracle <- rep(NA, T_dim * n_dim)
  XA_oracle <- matrix(NA, nrow = T_dim * n_dim, ncol = pA_vec[p])

  YB_oracle <- rep(NA, T_dim * n_dim)
  XB_oracle <- matrix(NA, nrow = T_dim * n_dim, ncol = pB_vec[p])

  if(p == 3){
    YC_oracle <- rep(NA, T_dim * n_dim)
    XC_oracle <- matrix(NA, nrow = T_dim * n_dim, ncol = pC)
  }

  for(l in 1:n_dim){
    indices <- ((l-1) * T_dim + 1):(l * T_dim)
    YA_oracle[indices] <- Pi %*% t(t(YA_tmp[indices]))
    XA_oracle[indices,] <- Pi %*% t(t(XA_tmp[indices,]))

    YB_oracle[indices] <- Pi %*% t(t(YB_tmp[indices]))
    XB_oracle[indices,] <- Pi %*% t(t(XB_tmp[indices,]))
    if(p == 3){
      YC_oracle[indices] <- Pi %*% t(t(YC_tmp[indices]))
      XC_oracle[indices,] <- Pi %*% t(t(XC_tmp[indices,]))
    }
  }

  # ############### Collect estimation results ##############
  # ## Lasso results
  # 1.  Estimated Pi - Lasso results
  resALasso <- hdcce::hdcce_estimator(data = list(x = XA_tmp, y = YA_tmp),
                                   obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01,
                                  variant = "Lasso", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)
  resBLasso <- hdcce::hdcce_estimator(data = list(x = XB_tmp, y = YB_tmp),
                                   obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01,
                                  variant = "Lasso", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)
  if(p == 3){
  resCLasso <- hdcce::hdcce_estimator(data = list(x = XC_tmp, y = YC_tmp),
                                  obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01,
                                  variant = "Lasso", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)
  }
  
  # 2. Oracle Lasso results
  tmp_fit_Lasso.cv <- glmnet::cv.glmnet(x = XA_oracle, y = YA_oracle, nfolds = n_Folds,
                                            foldid = fold_vec, family = "gaussian",
                                            alpha = 1, intercept = FALSE)
  resAOracleLasso <- stats::coef(tmp_fit_Lasso.cv, s = "lambda.min")[-1]

  tmp_fit_Lasso.cv <- glmnet::cv.glmnet(x = XB_oracle, y = YB_oracle, nfolds = n_Folds,
                                            foldid = fold_vec, family = "gaussian",
                                            alpha = 1, intercept = FALSE)
  resBOracleLasso <- stats::coef(tmp_fit_Lasso.cv, s = "lambda.min")[-1]
  
  if(p == 3){
  tmp_fit_Lasso.cv <- glmnet::cv.glmnet(x = XC_oracle, y = YC_oracle, nfolds = n_Folds,
                                            foldid = fold_vec, family = "gaussian",
                                            alpha = 1, intercept = FALSE)
  resCOracleLasso <- stats::coef(tmp_fit_Lasso.cv, s = "lambda.min")[-1]
  }


  # ## Least squares based result
  # 3. Oracle least squares
  resAOracleLS <- lm(YA_oracle ~ XA_oracle - 1)$coefficients
  resBOracleLS <- lm(YB_oracle ~ XB_oracle - 1)$coefficients

  # 4. Pi_hat projected least squares
  resALS <- hdcce::hdcce_estimator(data = list(x = XA_tmp, y = YA_tmp),
                                   obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01,
                                   variant = "LS", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)$coefs
  
  resBLS <- hdcce::hdcce_estimator(data = list(x = XB_tmp, y = YB_tmp),
                                   obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01,
                                   variant = "LS", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)$coefs
  # 5. Oracle Oracle LS
  S_A <- as.logical(beta_A)
  resAOracleOracleLS <- lm(YA_oracle ~ XA_oracle[ ,S_A] - 1)$coefficients 
  
  S_B <- as.logical(beta_B)
  resBOracleOracleLS <- lm(YB_oracle ~ XB_oracle[ ,S_B] - 1)$coefficients 

  if(p == 3){
    S_C <- as.logical(beta_C)
    resCOracleOracleLS <- lm(YC_oracle ~ XC_oracle[ ,S_C] - 1)$coefficients
  }
  
  # 6. Pesarans CCE Solution (Only applicable in scenario A)
  XA_bar <- matrix(NA, ncol = pA_vec[p], nrow = T_dim)
  YA_bar <- numeric(T_dim)
  
  for(t in 1:T_dim){
     indices <- seq(t, n_dim*T_dim, by = T_dim)
     XA_bar[t,] <- colMeans(XA_tmp[indices,])
     YA_bar[t] <- mean(YA_tmp[indices])
  }
  W_A <- cbind(XA_bar, YA_bar)
  PiA_pesaran <- diag(1, nrow = T_dim, ncol = T_dim) - W_A %*% solve(t(W_A) %*% W_A) %*% t(W_A)
  
  # Pesaran Projected Data
  YA_pesaran <- rep(NA, T_dim * n_dim)
  XA_pesaran<- matrix(NA, nrow = T_dim * n_dim, ncol = pA_vec[p])
  
  for(l in 1:n_dim){
    indices <- ((l-1) * T_dim + 1):(l * T_dim)
    YA_pesaran[indices] <- PiA_pesaran %*% t(t(YA_tmp[indices]))
    XA_pesaran[indices,] <- PiA_pesaran %*% t(t(XA_tmp[indices,]))
  }
  resAPesaran <- lm(YA_pesaran ~ XA_pesaran - 1)$coefficients
  
  


 # 7. Collect results for High K, i.e. overestimate its value
  if(p   >  1 && count == 1){
  HIGHresALS <- hdcce::hdcce_estimator(data = list(x = XA_tmp, y = YA_tmp),
                                   obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01, NFACTORS = 6,
                                  variant = "LS", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)
  HIGHresBLS <- hdcce::hdcce_estimator(data = list(x = XB_tmp, y = YB_tmp),
                                    obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01, NFACTORS = 6,
                                  variant = "LS", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)
  
  
  HIGHresALasso <- hdcce::hdcce_estimator(data = list(x = XA_tmp, y = YA_tmp),
                                    obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01, NFACTORS = 6,
                                  variant = "Lasso", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)
  
  HIGHresBLasso <- hdcce::hdcce_estimator(data = list(x = XB_tmp, y = YB_tmp),
                                    obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01, NFACTORS = 6,
                                  variant = "Lasso", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)
 if(p == 3){
 HIGHresCLasso <- hdcce::hdcce_estimator(data = list(x = XC_tmp, y = YC_tmp),
                                    obs_N = n_dim, obs_T = T_dim, TRUNC = 0.01, NFACTORS = 6,
                                  variant = "Lasso", NFOLDS = n_Folds, 
                                   foldid = fold_vec, scree_plot = FALSE)
 }else{
   HIGHresCLasso <- NULL
    HIGHresCLS <- NULL
 }
 }else{
    HIGHresALasso <- NULL
    HIGHresALS <- NULL
    
    HIGHresBLasso <- NULL
    HIGHresBLS <- NULL
    
    HIGHresCLasso <- NULL
    HIGHresCLS <- NULL
  }

 
 # 8. Inference results
  statisticA <- numeric(3)
  statisticB <- numeric(3)
  if(p == 3){
  statisticC <- numeric(3)
  }

  for (k in 1:3) {
   resAInference <- hdcce::hdcce_inference(data = list(x = XA_tmp, y = YA_INFERENCE_tmp[,k]), obs_N = n_dim, obs_T = T_dim,  foldid = fold_vec, COEF_INDEX = 1)

  resBInference <- hdcce::hdcce_inference(data = list(x = XB_tmp, y = YB_INFERENCE_tmp[,k]), obs_N = n_dim, obs_T = T_dim,  foldid = fold_vec, COEF_INDEX = 1)

  if(p == 3){
    resCInference <- hdcce::hdcce_inference(data = list(x = XC_tmp, y = YC_INFERENCE_tmp[,k]), obs_N = n_dim, obs_T = T_dim, foldid = fold_vec, COEF_INDEX  = 1)
  }

  statisticA[k] <- (1/resAInference$Avar)*resAInference$coef_despar
  statisticB[k] <- (1/resBInference$Avar)*resBInference$coef_despar
  if(p == 3){
    statisticC[k] <- (1/resCInference$Avar)*resCInference$coef_despar
  }
}
  
  
  
  ### Collect all results for A, B and C ###
  results_A <- list(TestStatistic = statisticA, Lasso = resALasso, OracleLasso = resAOracleLasso, LS = 
                      resALS, OracleLS = resAOracleLS, OracleOracleLS = resAOracleOracleLS, 
                    PesaranCCE = resAPesaran, HighKLasso = HIGHresALasso, HighKLS = HIGHresALS)
  results_B <- list(TestStatistic = statisticB, Lasso = resBLasso, OracleLasso = resBOracleLasso, LS = resBLS,
                    OracleLS = resBOracleLS, OracleOracleLS = resBOracleOracleLS, HighKLasso = HIGHresBLasso, HighKLS = HIGHresBLS)
  
  if(p == 3){
  results_C <- list(TestStatistic = statisticC, Lasso = resCLasso, OracleLasso = resCOracleLasso, OracleOracleLS = resCOracleOracleLS, HighKLasso = HIGHresCLasso)
  }else{
    results_C <- NULL
  }
  
  p_res_K[[p]] <- list(results_A, results_B, results_C)
 
  
 }
 
 gamma_res[[count]] <- p_res_K 
 count <- count + 1
}
 gamma_res 
} 
stopCluster(cl)
tictoc::toc()
```


## Count estimated numbers of factors K


```{r}

estimated_KhatA <- matrix(NA, nrow = 3, ncol = 18)
estimated_KhatB <- matrix(NA, nrow = 3, ncol = 18)
estimated_KhatC <- numeric(16)

for (gamma in 1:2) {
  greater <- 0
  for (p in 1:3) {
  tmpestimated_KhatA <- numeric(9)
  tmpestimated_KhatB <- numeric(9)
  tmpestimated_KhatC <- numeric(9)
    for (sim in 1:N_Sim){
      # if(results_Factors[[sim]][[gamma]][[p]][[2]][["Lasso"]][["K_hat"]] > 8){
      # print(results_Factors[[sim]][[gamma]][[p]][[2]][["Lasso"]][["K_hat"]])
      # }
      for (j in 1:8) {
      if(results_Factors[[sim]][[gamma]][[p]][[1]][["Lasso"]][["K_hat"]] == j){
        tmpestimated_KhatA[j] <- tmpestimated_KhatA[j] + results_Factors[[sim]][[gamma]][[p]][[1]][["Lasso"]][["K_hat"]]
      }

      if(results_Factors[[sim]][[gamma]][[p]][[2]][["Lasso"]][["K_hat"]] == j){
         tmpestimated_KhatB[j] <- tmpestimated_KhatB[j] + results_Factors[[sim]][[gamma]][[p]][[2]][["Lasso"]][["K_hat"]]
      }
      if(p == 3){
      if(results_Factors[[sim]][[gamma]][[p]][[3]][["Lasso"]][["K_hat"]]  == j){
         tmpestimated_KhatC[j] <- tmpestimated_KhatC[j] + results_Factors[[sim]][[gamma]][[p]][[3]][["Lasso"]][["K_hat"]]
      }
      }
    }
    }
    estimated_KhatA[p, ((gamma-1)*9+1):(9*gamma)] <- tmpestimated_KhatA / c(1,2,3,4,5,6,7,8,9)
    estimated_KhatB[p, ((gamma-1)*9+1):(9*gamma)]<- tmpestimated_KhatB / c(1,2,3,4,5,6,7,8,9)
    if(p == 3){
    estimated_KhatC[((gamma-1)*9+1):(9*gamma)]<- tmpestimated_KhatC / c(1,2,3,4,5,6,7,8,9)
    }
  }
}
```




```{r}
library(stargazer)
stargazer(rbind(estimated_KhatA, estimated_KhatB, estimated_KhatC))
```










## Rearrange result list to obtain accuracy plots gamma = 1,2 will determine whether eigenvalues of factor loadings are not spiked or spiked respectively.


```{r}
gamma <- 1
T_dim <- 15
  LassoA <-  vector(mode = 'list', length = 3)
  OracleLassoA <-  vector(mode = 'list', length = 3)
  LSA <- vector(mode = 'list', length = 3)
  OracleLSA <- vector(mode = 'list', length = 3)
  OracleOracleLSA <-  vector(mode = 'list', length = 3)
  PesaranCCE <-  vector(mode = 'list', length = 3)

  LassoB <-  vector(mode = 'list', length = 3)
  OracleLassoB <- vector(mode = 'list', length = 3)
  LSB <-  vector(mode = 'list', length = 3)
  OracleLSB <-  vector(mode = 'list', length = 3)
  OracleOracleLSB <-  vector(mode = 'list', length = 3)


  LassoC <-  vector(mode = 'list', length = 1)
  OracleLassoC <- vector(mode = 'list', length = 1)
  OracleOracleLSC <-  vector(mode = 'list', length = 1)



  for (p in 1:3) {
      tmpLassoA <- numeric(pA_vec[p])
      tmpOracleLassoA <- numeric(pA_vec[p])
      tmpLSA <- numeric(pA_vec[p])
      tmpOracleLSA <- numeric(pA_vec[p])
      if(T_dim == 15){
        if(p == 1){
          tmpOracleOracleLSA<-numeric(7)
        }else{
          tmpOracleOracleLSA<-numeric(10)
        }
      }else{
          tmpOracleOracleLSA<-numeric(10)
        }


      tmpPesaranCCE <- numeric(pA_vec[p])

      tmpLassoB <- numeric(pB_vec[p])
      tmpOracleLassoB <- numeric(pB_vec[p])
      tmpLSB <- numeric(pB_vec[p])
      tmpOracleLSB<- numeric(pB_vec[p])
      tmpOracleOracleLSB <- numeric(10)

      if(p == 3){
      tmpLassoC <- numeric(pC)
      tmpOracleLassoC <- numeric(pC)
      tmpOracleOracleLSC <- numeric(10)
      }

    for (sim in 1:N_Sim) {
      tmpLassoA <- rbind(tmpLassoA, results_Factors[[sim]][[gamma]][[p]][[1]][["Lasso"]]$coefs)
      tmpOracleLassoA <- rbind(tmpOracleLassoA, results_Factors[[sim]][[gamma]][[p]][[1]][["OracleLasso"]])
      tmpLSA<-rbind(tmpLSA, results_Factors[[sim]][[gamma]][[p]][[1]]$LS)
      tmpOracleLSA <- rbind(tmpOracleLSA, results_Factors[[sim]][[gamma]][[p]][[1]][["OracleLS"]])
      tmpOracleOracleLSA<- rbind(tmpOracleOracleLSA, results_Factors[[sim]][[gamma]][[p]][[1]][["OracleOracleLS"]])
      tmpPesaranCCE <- rbind(tmpPesaranCCE, results_Factors[[sim]][[gamma]][[p]][[1]][["PesaranCCE"]])

      tmpLassoB <- rbind(tmpLassoB, results_Factors[[sim]][[gamma]][[p]][[2]][["Lasso"]]$coefs)
      tmpOracleLassoB <- rbind(tmpOracleLassoB, results_Factors[[sim]][[gamma]][[p]][[2]][["OracleLasso"]])
      tmpLSB <- rbind(tmpLSB, results_Factors[[sim]][[gamma]][[p]][[2]]$LS)
      tmpOracleLSB<- rbind(tmpOracleLSB,  results_Factors[[sim]][[gamma]][[p]][[2]][["OracleLS"]])
      tmpOracleOracleLSB <- rbind(tmpOracleOracleLSB, results_Factors[[sim]][[gamma]][[p]][[2]][["OracleOracleLS"]])

      if(p == 3){
      tmpLassoC <- rbind(tmpLassoC, results_Factors[[sim]][[gamma]][[p]][[3]][["Lasso"]]$coefs)
      tmpOracleLassoC <- rbind(tmpOracleLassoC,results_Factors[[sim]][[gamma]][[p]][[3]][["OracleLasso"]])
      tmpOracleOracleLSC <- rbind(tmpOracleOracleLSC, results_Factors[[sim]][[gamma]][[p]][[3]][["OracleOracleLS"]])
      }
    }
    LassoA[[p]] <-  tmpLassoA[-1,]
    OracleLassoA[[p]] <- tmpOracleLassoA[-1,]
    LSA[[p]] <- tmpLSA[-1,]
    OracleLSA[[p]] <- tmpOracleLSA[-1,]
    OracleOracleLSA[[p]] <- tmpOracleOracleLSA[-1,]
    PesaranCCE[[p]] <- tmpPesaranCCE[-1,]

    LassoB[[p]] <- tmpLassoB[-1,]
    OracleLassoB[[p]] <- tmpOracleLassoB[-1,]
    LSB[[p]] <- tmpLSB[-1,]
    OracleLSB[[p]] <- tmpOracleLSB[-1,]
    OracleOracleLSB[[p]] <- tmpOracleOracleLSB[-1,]
    if(p == 3){
    LassoC[[1]] <- tmpLassoC[-1,]
    OracleLassoC[[1]] <- tmpOracleLassoC[-1,]
    OracleOracleLSC[[1]] <- tmpOracleOracleLSC[-1,]
    }
}
```






## Produce boxplots
```{r}
library(latex2exp)
##################### Boxplots for T = 15 ############################
## Scenario A
# Boxplot for group representatives for each estimator
col_vec2 <- c("green", "blue", "red", "magenta", "bisque", rep(c("green", "blue", "red", "yellow", "magenta", "cyan", "bisque", "darkorange"), 4))
col_vec_A <-  c("green", "blue", "red", "magenta", "bisque", rep(c("green", "blue", "red", "yellow", "magenta", "cyan", "bisque", "darkorange"), 5))

col_vec_ASMALLT <- c("green", "blue", "red", "magenta", "bisque")

boxplot(data.frame(OracleOracleLSA[[1]][,1]-rep(c_val, N_Sim), OracleOracleLSA[[1]][,2]-rep(c_val, N_Sim), OracleOracleLSA[[1]][,3]-rep(c_val, N_Sim), OracleOracleLSA[[1]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSA[[1]][,6]-rep(c_val, N_Sim), PesaranCCE[[1]][,1]-rep(c_val, N_Sim), 
                  PesaranCCE[[1]][,2]-rep(c_val, N_Sim),  PesaranCCE[[1]][,3]-rep(c_val, N_Sim), PesaranCCE[[1]][,4]-rep(c_val, N_Sim), PesaranCCE[[1]][,6]-rep(c_val, N_Sim), 
        OracleLSA[[1]][,1]-rep(c_val, N_Sim), OracleLSA[[1]][,2]-rep(c_val, N_Sim),  OracleLSA[[1]][,3]-rep(c_val, N_Sim), OracleLSA[[1]][,4]-rep(c_val, N_Sim), OracleLSA[[1]][,6]-rep(c_val, N_Sim), 
                  LSA[[1]][,1]-rep(c_val, N_Sim), LSA[[1]][,2]-rep(c_val, N_Sim), LSA[[1]][,3]-rep(c_val, N_Sim), LSA[[1]][,4]-rep(c_val, N_Sim), LSA[[1]][,6]-rep(c_val, N_Sim),
                  OracleLassoA[[1]][,1]-rep(c_val, N_Sim), OracleLassoA[[1]][,2]-rep(c_val, N_Sim), OracleLassoA[[1]][,3]-rep(c_val, N_Sim), OracleLassoA[[1]][,4]-rep(c_val, N_Sim), OracleLassoA[[1]][,6]-rep(c_val, N_Sim), LassoA[[1]][,1]-rep(c_val, N_Sim), LassoA[[1]][,2]-rep(c_val, N_Sim), LassoA[[1]][,3]-rep(c_val, N_Sim), LassoA[[1]][,4]-rep(c_val, N_Sim), LassoA[[1]][,6]-rep(c_val, N_Sim)), yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,10), seq(12,16), seq(18,22), seq(24,28), seq(30, 34)),
        col = col_vec_ASMALLT, cex = 0.2, boxwex = 0.5, lwd = 0.8, whisklty = 1)
title("p =  7",line=0.3, cex.main = 1)
axis(2, las =0, at = c(1, 8, 15, 21, 26, 32), labels = c(TeX(r"(LS-O$^2$)"), "CCE","LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))

abline(h = 5, lwd = 1)
abline(h = 11, lwd = 1)
abline(h = 17, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 29, lwd = 1)
abline(v = 0)


        

## Scenario B
# Boxplot for group representatives for each estimator
boxplot(data.frame(OracleOracleLSB[[1]][,1]-rep(c_val, N_Sim), OracleOracleLSB[[1]][,2]-rep(c_val, N_Sim), OracleOracleLSB[[1]][,3]-rep(c_val, N_Sim), OracleOracleLSB[[1]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[1]][,6]-rep(c_val, N_Sim), OracleLSB[[1]][,1]-rep(c_val, N_Sim), OracleLSB[[1]][,2]-rep(c_val, N_Sim),  OracleLSB[[1]][,3]-rep(c_val, N_Sim), OracleLSB[[1]][,5], OracleLSB[[1]][,(2+10)]-rep(c_val, N_Sim), 
                  OracleLSB[[1]][,(5+10)], OracleLSB[[1]][,(2+2*10)]-rep(c_val, N_Sim),OracleLSB[[1]][,(5+2*10)], LSB[[1]][,1]-rep(c_val, N_Sim), LSB[[1]][,2]-rep(c_val, N_Sim), LSB[[1]][,3]-rep(c_val, N_Sim), LSB[[1]][,5], LSB[[1]][,(2+10)]-rep(c_val, N_Sim), LSB[[1]][,(5+10)], LSB[[1]][,(2+2*10)]-rep(c_val, N_Sim), 
                  LSB[[1]][,(5+2*10)],
                  OracleLassoB[[1]][,1]-rep(c_val, N_Sim), OracleLassoB[[1]][,2]-rep(c_val, N_Sim), OracleLassoB[[1]][,3]-rep(c_val, N_Sim), OracleLassoB[[1]][,5], OracleLassoB[[1]][,(2+10)]-rep(c_val, N_Sim), 
                  OracleLassoB[[1]][,(5+10)], OracleLassoB[[1]][,(2+2*10)]-rep(c_val, N_Sim), OracleLassoB[[1]][,(5+2*10)], 
                  LassoB[[1]][,1]-rep(c_val, N_Sim), LassoB[[1]][,2]-rep(c_val, N_Sim), LassoB[[1]][,3]-rep(c_val, N_Sim), LassoB[[1]][,5], LassoB[[1]][,(2+10)]-rep(c_val, N_Sim), LassoB[[1]][,(5+10)], 
                   LassoB[[1]][,(2+2*10)]-rep(c_val, N_Sim), LassoB[[1]][,(5+2*10)]),
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40)),
        col = col_vec2, cex = 0.2, boxwex = 0.6, lwd = 0.8, whisklty = 1)
title("p =  31",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19, 28, 37), labels = c(TeX(r"(LS-O$^2$)"), "LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(v = 0)

## Scenario C
boxplot(data.frame(OracleOracleLSC[[1]][,1]-rep(c_val, N_Sim), OracleOracleLSC[[1]][,2]-rep(c_val, N_Sim), OracleOracleLSC[[1]][,3]-rep(c_val, N_Sim), 
                  OracleOracleLSC[[1]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSC[[1]][,6]-rep(c_val, N_Sim), OracleLassoC[[1]][,1]-rep(c_val, N_Sim), OracleLassoC[[1]][,2]-rep(c_val, N_Sim), OracleLassoC[[1]][,3]-rep(c_val, N_Sim), OracleLassoC[[1]][,5], 
                  OracleLassoC[[1]][,(2+300)]-rep(c_val, N_Sim), 
                  OracleLassoC[[1]][,(5+300)], OracleLassoC[[1]][,(2+2*300)]-rep(c_val, N_Sim), OracleLassoC[[1]][,(5+2*300)], 
                  LassoC[[1]][,1]-rep(c_val, N_Sim), LassoC[[1]][,2]-rep(c_val, N_Sim), LassoC[[1]][,3]-rep(c_val, N_Sim), LassoC[[1]][,5], LassoC[[1]][,(2+300)]-rep(c_val, N_Sim), 
                   LassoC[[1]][,(5+300)], LassoC[[1]][,(2+2*300)]-rep(c_val, N_Sim), LassoC[[1]][,(5+2*300)]),
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22)), col = col_vec2, cex = 0.2, boxwex = 0.4, lwd = 0.8, whisklty = 1)
title("p =  901",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19), labels = c(TeX(r"(LS-O$^2$)"), "L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(v = 0)



# p = 2

## Scenario A
# Boxplot for group representatives for each estimator

boxplot(data.frame(OracleOracleLSA[[2]][,1]-rep(c_val, N_Sim), OracleOracleLSA[[2]][,2]-rep(c_val, N_Sim), OracleOracleLSA[[2]][,3]-rep(c_val, N_Sim), OracleOracleLSA[[2]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSA[[2]][,6]-rep(c_val, N_Sim),  
                  PesaranCCE[[2]][,1]-rep(c_val, N_Sim), PesaranCCE[[2]][,2]-rep(c_val, N_Sim),  PesaranCCE[[2]][,3]-rep(c_val, N_Sim), PesaranCCE[[2]][,5]-rep(c_val, N_Sim), PesaranCCE[[2]][,8]-rep(c_val, N_Sim),
                  OracleLSA[[2]][,1]-rep(c_val, N_Sim), OracleLSA[[2]][,2]-rep(c_val, N_Sim),  OracleLSA[[2]][,3]-rep(c_val, N_Sim), OracleLSA[[2]][,5]-rep(c_val, N_Sim), OracleLSA[[2]][,8]-rep(c_val, N_Sim),
                  LSA[[2]][,1]-rep(c_val, N_Sim), LSA[[2]][,2]-rep(c_val, N_Sim), LSA[[2]][,3]-rep(c_val, N_Sim), LSA[[2]][,5]-rep(c_val, N_Sim), LSA[[2]][,8]-rep(c_val, N_Sim),
                  OracleLassoA[[2]][,1]-rep(c_val, N_Sim), OracleLassoA[[2]][,2]-rep(c_val, N_Sim), OracleLassoA[[2]][,3]-rep(c_val, N_Sim), OracleLassoA[[2]][,5]-rep(c_val, N_Sim), OracleLassoA[[2]][,8]-rep(c_val, N_Sim), 
                  LassoA[[2]][,1]-rep(c_val, N_Sim), LassoA[[2]][,2]-rep(c_val, N_Sim), LassoA[[2]][,3]-rep(c_val, N_Sim), LassoA[[2]][,5]-rep(c_val, N_Sim), LassoA[[2]][,8]-rep(c_val, N_Sim)),
                
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,10), seq(12,16), seq(18,22), seq(24,28), seq(30, 34)),
        col = col_vec_ASMALLT, cex = 0.2, boxwex = 0.5, lwd = 0.8, whisklty = 1)
title("p =  10",line=0.3, cex.main = 1)
axis(2, las =0, at = c(1, 8, 15, 21, 26, 32), labels = c(TeX(r"(LS-O$^2$)"), "CCE","LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))

abline(h = 5, lwd = 1)
abline(h = 11, lwd = 1)
abline(h = 17, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 29, lwd = 1)
abline(v = 0)


        

## Scenario B
# Boxplot for group representatives for each estimator
boxplot(data.frame(OracleOracleLSB[[2]][,1]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,2]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,3]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,5]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[2]][,8]-rep(c_val, N_Sim), OracleLSB[[2]][,1]-rep(c_val, N_Sim), OracleLSB[[2]][,2]-rep(c_val, N_Sim),  OracleLSB[[2]][,3]-rep(c_val, N_Sim),  OracleLSB[[2]][,5], OracleLSB[[2]][,(2+50)]-rep(c_val, N_Sim),  
                  OracleLSB[[2]][,(5+50)],  OracleLSB[[2]][,(2+2*50)]-rep(c_val, N_Sim), OracleLSB[[2]][,(5+2*50)], LSB[[2]][,1]-rep(c_val, N_Sim), LSB[[2]][,2]-rep(c_val, N_Sim), LSB[[2]][,3]-rep(c_val, N_Sim), LSB[[2]][,5], LSB[[2]][,(2+50)]-rep(c_val, N_Sim), LSB[[2]][,(5+50)], LSB[[2]][,(2+2*50)]-rep(c_val, N_Sim), 
                  LSB[[2]][,(5+2*50)], OracleLassoB[[2]][,1]-rep(c_val, N_Sim), OracleLassoB[[2]][,2]-rep(c_val, N_Sim), OracleLassoB[[2]][,3]-rep(c_val, N_Sim), OracleLassoB[[2]][,5], OracleLassoB[[2]][,(2+50)]-rep(c_val, N_Sim), 
                  OracleLassoB[[2]][,(5+50)], OracleLassoB[[2]][,(2+2*50)]-rep(c_val, N_Sim), OracleLassoB[[2]][,(5+2*50)],  LassoB[[2]][,1]-rep(c_val, N_Sim), LassoB[[2]][,2]-rep(c_val, N_Sim), LassoB[[2]][,3]-rep(c_val, N_Sim), LassoB[[2]][,5], LassoB[[2]][,(2+50)]-rep(c_val, N_Sim), LassoB[[2]][,(5+50)], 
                   LassoB[[2]][,(2+2*50)]-rep(c_val, N_Sim), LassoB[[2]][,(5+2*50)]), 
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40)),
        col = col_vec2, cex = 0.2, boxwex = 0.6, lwd = 0.8, whisklty = 1)
title("p =  151",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19, 28, 37), labels = c(TeX(r"(LS-O$^2$)"), "LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(v = 0)




# p = 3

## Scenario A
# Boxplot for group representatives for each estimator




boxplot(data.frame( 
                  OracleOracleLSA[[3]][,1]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,2]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,3]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSA[[3]][,6]-rep(c_val, N_Sim), PesaranCCE[[3]][,1]-rep(c_val, N_Sim),  PesaranCCE[[3]][,2]-rep(c_val, N_Sim),  PesaranCCE[[3]][,3]-rep(c_val, N_Sim), PesaranCCE[[3]][,5], PesaranCCE[[3]][,6]-rep(c_val, N_Sim), 
                  PesaranCCE[[3]][,9], PesaranCCE[[3]][,10]-rep(c_val, N_Sim), PesaranCCE[[3]][,13], OracleLSA[[3]][,1]-rep(c_val, N_Sim), OracleLSA[[3]][,2]-rep(c_val, N_Sim),  OracleLSA[[3]][,3]-rep(c_val, N_Sim), OracleLSA[[3]][,5], OracleLSA[[3]][,6]-rep(c_val, N_Sim), 
                  OracleLSA[[3]][,9], OracleLSA[[3]][,10]-rep(c_val, N_Sim),OracleLSA[[3]][,13], LSA[[3]][,1]-rep(c_val, N_Sim), LSA[[3]][,2]-rep(c_val, N_Sim), LSA[[3]][,3]-rep(c_val, N_Sim), LSA[[3]][,5], LSA[[3]][,6]-rep(c_val, N_Sim), LSA[[3]][,9], LSA[[3]][,10]-rep(c_val, N_Sim), 
                  LSA[[3]][,13], OracleLassoA[[3]][,1]-rep(c_val, N_Sim), OracleLassoA[[3]][,2]-rep(c_val, N_Sim), OracleLassoA[[3]][,3]-rep(c_val, N_Sim), OracleLassoA[[3]][,5], OracleLassoA[[3]][,6]-rep(c_val, N_Sim), OracleLassoA[[3]][,9], OracleLassoA[[3]][,10]-rep(c_val, N_Sim), OracleLassoA[[3]][,13], LassoA[[3]][,1]-rep(c_val, N_Sim), LassoA[[3]][,2]-rep(c_val, N_Sim), LassoA[[3]][,3]-rep(c_val, N_Sim), LassoA[[3]][,5], LassoA[[3]][,6]-rep(c_val, N_Sim), LassoA[[3]][,9], 
                   LassoA[[3]][,10]-rep(c_val, N_Sim), LassoA[[3]][,13]),
                 
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40), seq(42, 49)),
        col = col_vec_A, cex = 0.2, boxwex = 0.7, lwd = 0.8, whisklty = 1)
title("p =  13",line=0.3, cex.main = 1)
axis(2, las =0, at = c(1, 10, 19, 27, 37, 46), labels = c(TeX(r"(LS-O$^2$)"), "CCE","LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))

abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(h = 41, lwd = 1)
abline(v = 0)
        

## Scenario B
# Boxplot for group representatives for each estimator
boxplot(data.frame( OracleOracleLSB[[3]][,1]-rep(c_val, N_Sim), OracleOracleLSB[[3]][,2]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[3]][,3]-rep(c_val, N_Sim), OracleOracleLSB[[3]][,5]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[3]][,10]-rep(c_val, N_Sim), OracleLSB[[3]][,1]-rep(c_val, N_Sim), OracleLSB[[3]][,2]-rep(c_val, N_Sim),  
                  OracleLSB[[3]][,3]-rep(c_val, N_Sim), OracleLSB[[3]][,5], 
                  OracleLSB[[3]][,(2+100)]-rep(c_val,N_Sim),  
                  OracleLSB[[3]][,(5+100)], OracleLSB[[3]][,(2+2*100)]-rep(c_val, N_Sim), OracleLSB[[3]][,(5+2*100)], LSB[[3]][,1]-rep(c_val, N_Sim), LSB[[3]][,2]-rep(c_val, N_Sim), LSB[[3]][,3]-rep(c_val, N_Sim), 
                  LSB[[3]][,5], LSB[[3]][,(2+100)]-rep(c_val, N_Sim), LSB[[3]][,(5+100)], 
                  LSB[[3]][,(2+2*100)]-rep(c_val, N_Sim), 
                  LSB[[3]][,(5+2*100)], 
                  OracleLassoB[[3]][,1]-rep(c_val, N_Sim), OracleLassoB[[3]][,2]-rep(c_val, N_Sim), 
                  OracleLassoB[[3]][,3]-rep(c_val, N_Sim), OracleLassoB[[3]][,5], 
                  OracleLassoB[[3]][,(2+100)]-rep(c_val, N_Sim), OracleLassoB[[3]][,(5+100)], 
                  OracleLassoB[[3]][,(2+2*100)]-rep(c_val, N_Sim), OracleLassoB[[3]][,(5+2*100)],  LassoB[[3]][,1]-rep(c_val, N_Sim), LassoB[[3]][,2]-rep(c_val, N_Sim), LassoB[[3]][,3]-rep(c_val, N_Sim), 
                   LassoB[[3]][,5], LassoB[[3]][,(2+100)]-rep(c_val, N_Sim), LassoB[[3]][,(5+100)], 
                   LassoB[[3]][,(2+2*100)]-rep(c_val, N_Sim), LassoB[[3]][,(5+2*100)]), 
                  
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40)),
        col = col_vec2, cex = 0.2, boxwex = 0.6, lwd = 0.8, whisklty = 1)
title("p =  301",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19, 28, 37), labels = c(TeX(r"(LS-O$^2$)"), "LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(v = 0)

```






```{r}

################ Boxplots for T = 50 ###########################
# p = 1

## Scenario A
# Boxplot for group representatives for each estimator
col_vec2 <- c("green", "blue", "red", "magenta", "bisque", rep(c("green", "blue", "red", "yellow", "magenta", "cyan", "bisque", "darkorange"), 4))
col_vec_A <-  c("green", "blue", "red", "magenta", "bisque", rep(c("green", "blue", "red", "yellow", "magenta", "cyan", "bisque", "darkorange"), 5))

boxplot(data.frame(OracleOracleLSA[[1]][,2]-rep(c_val, N_Sim), OracleOracleLSA[[1]][,3]-rep(c_val, N_Sim), OracleOracleLSA[[1]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSA[[1]][,6]-rep(c_val, N_Sim), PesaranCCE[[1]][,1]-rep(c_val, N_Sim), 
                  PesaranCCE[[1]][,2]-rep(c_val, N_Sim),  PesaranCCE[[1]][,3]-rep(c_val, N_Sim), PesaranCCE[[1]][,5], PesaranCCE[[1]][,(2+5)]-rep(c_val, N_Sim), 
                  PesaranCCE[[1]][,(5+5)], PesaranCCE[[1]][,(2+2*5)]-rep(c_val, N_Sim),PesaranCCE[[1]][,(5+2*5)], 
        OracleLSA[[1]][,1]-rep(c_val, N_Sim), OracleLSA[[1]][,2]-rep(c_val, N_Sim),  OracleLSA[[1]][,3]-rep(c_val, N_Sim), OracleLSA[[1]][,5], OracleLSA[[1]][,(2+5)]-rep(c_val, N_Sim), 
                  OracleLSA[[1]][,(5+5)], OracleLSA[[1]][,(2+2*5)]-rep(c_val, N_Sim),OracleLSA[[1]][,(5+2*5)],
                  OracleOracleLSA[[1]][,1]-rep(c_val, N_Sim), 
                  LSA[[1]][,1]-rep(c_val, N_Sim), LSA[[1]][,2]-rep(c_val, N_Sim), LSA[[1]][,3]-rep(c_val, N_Sim), LSA[[1]][,5], LSA[[1]][,(2+5)]-rep(c_val, N_Sim), LSA[[1]][,(5+5)], LSA[[1]][,(2+2*5)]-rep(c_val, N_Sim), 
                  LSA[[1]][,(5+2*5)],
                  OracleLassoA[[1]][,1]-rep(c_val, N_Sim), OracleLassoA[[1]][,2]-rep(c_val, N_Sim), OracleLassoA[[1]][,3]-rep(c_val, N_Sim), OracleLassoA[[1]][,5], OracleLassoA[[1]][,(2+5)]-rep(c_val, N_Sim), 
                  OracleLassoA[[1]][,(5+5)], OracleLassoA[[1]][,(2+2*5)]-rep(c_val, N_Sim), OracleLassoA[[1]][,(5+2*5)], 
                  LassoA[[1]][,1]-rep(c_val, N_Sim), LassoA[[1]][,2]-rep(c_val, N_Sim), LassoA[[1]][,3]-rep(c_val, N_Sim), LassoA[[1]][,5], LassoA[[1]][,(2+5)]-rep(c_val, N_Sim), LassoA[[1]][,(5+5)], 
                   LassoA[[1]][,(2+2*5)]-rep(c_val, N_Sim), LassoA[[1]][,(5+2*5)]),
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40), seq(42, 49)),
        col = col_vec_A, cex = 0.2, boxwex = 0.7, lwd = 0.8, whisklty = 1)
title("p =  16",line=0.3, cex.main = 1)
axis(2, las =0, at = c(1, 10, 19, 27, 37, 46), labels = c(TeX(r"(LS-O$^2$)"), "CCE","LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))

abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(h = 41, lwd = 1)
abline(v = 0)


        

## Scenario B
# Boxplot for group representatives for each estimator
boxplot(data.frame(OracleOracleLSB[[1]][,1]-rep(c_val, N_Sim), OracleOracleLSB[[1]][,2]-rep(c_val, N_Sim), OracleOracleLSB[[1]][,3]-rep(c_val, N_Sim), OracleOracleLSB[[1]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[1]][,6]-rep(c_val, N_Sim), OracleLSB[[1]][,1]-rep(c_val, N_Sim), OracleLSB[[1]][,2]-rep(c_val, N_Sim),  OracleLSB[[1]][,3]-rep(c_val, N_Sim), OracleLSB[[1]][,5], OracleLSB[[1]][,(2+30)]-rep(c_val, N_Sim), 
                  OracleLSB[[1]][,(5+30)], OracleLSB[[1]][,(2+2*30)]-rep(c_val, N_Sim),OracleLSB[[1]][,(5+2*30)], LSB[[1]][,1]-rep(c_val, N_Sim), LSB[[1]][,2]-rep(c_val, N_Sim), LSB[[1]][,3]-rep(c_val, N_Sim), LSB[[1]][,5], LSB[[1]][,(2+30)]-rep(c_val, N_Sim), LSB[[1]][,(5+30)], LSB[[1]][,(2+2*30)]-rep(c_val, N_Sim), 
                  LSB[[1]][,(5+2*30)],
                  OracleLassoB[[1]][,1]-rep(c_val, N_Sim), OracleLassoB[[1]][,2]-rep(c_val, N_Sim), OracleLassoB[[1]][,3]-rep(c_val, N_Sim), OracleLassoB[[1]][,5], OracleLassoB[[1]][,(2+30)]-rep(c_val, N_Sim), 
                  OracleLassoB[[1]][,(5+30)], OracleLassoB[[1]][,(2+2*30)]-rep(c_val, N_Sim), OracleLassoB[[1]][,(5+2*30)], 
                  LassoB[[1]][,1]-rep(c_val, N_Sim), LassoB[[1]][,2]-rep(c_val, N_Sim), LassoB[[1]][,3]-rep(c_val, N_Sim), LassoB[[1]][,5], LassoB[[1]][,(2+30)]-rep(c_val, N_Sim), LassoB[[1]][,(5+30)], 
                   LassoB[[1]][,(2+2*30)]-rep(c_val, N_Sim), LassoB[[1]][,(5+2*30)]),
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40)),
        col = col_vec2, cex = 0.2, boxwex = 0.6, lwd = 0.8, whisklty = 1)
title("p =  91",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19, 28, 37), labels = c(TeX(r"(LS-O$^2$)"), "LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(v = 0)

## Scenario C
boxplot(data.frame(OracleOracleLSC[[1]][,1]-rep(c_val, N_Sim), OracleOracleLSC[[1]][,2]-rep(c_val, N_Sim), OracleOracleLSC[[1]][,3]-rep(c_val, N_Sim), 
                  OracleOracleLSC[[1]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSC[[1]][,6]-rep(c_val, N_Sim), OracleLassoC[[1]][,1]-rep(c_val, N_Sim), OracleLassoC[[1]][,2]-rep(c_val, N_Sim), OracleLassoC[[1]][,3]-rep(c_val, N_Sim), OracleLassoC[[1]][,5], 
                  OracleLassoC[[1]][,(2+1000)]-rep(c_val, N_Sim), 
                  OracleLassoC[[1]][,(5+1000)], OracleLassoC[[1]][,(2+2*1000)]-rep(c_val, N_Sim), OracleLassoC[[1]][,(5+2*1000)], 
                  LassoC[[1]][,1]-rep(c_val, N_Sim), LassoC[[1]][,2]-rep(c_val, N_Sim), LassoC[[1]][,3]-rep(c_val, N_Sim), LassoC[[1]][,5], LassoC[[1]][,(2+1000)]-rep(c_val, N_Sim), 
                   LassoC[[1]][,(5+1000)], LassoC[[1]][,(2+2*1000)]-rep(c_val, N_Sim), LassoC[[1]][,(5+2*1000)]),
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22)), col = col_vec2, cex = 0.2, boxwex = 0.4, lwd = 0.8, whisklty = 1)
title("p =  3001",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19), labels = c(TeX(r"(LS-O$^2$)"), "L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(v = 0)



# p = 2

## Scenario A
# Boxplot for group representatives for each estimator

boxplot(data.frame(OracleOracleLSA[[2]][,1]-rep(c_val, N_Sim), OracleOracleLSA[[2]][,2]-rep(c_val, N_Sim), OracleOracleLSA[[2]][,3]-rep(c_val, N_Sim), OracleOracleLSA[[2]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSA[[2]][,6]-rep(c_val, N_Sim),  
                  PesaranCCE[[2]][,1]-rep(c_val, N_Sim), PesaranCCE[[2]][,2]-rep(c_val, N_Sim),  PesaranCCE[[2]][,3]-rep(c_val, N_Sim), PesaranCCE[[2]][,5], PesaranCCE[[2]][,(2+10)]-rep(c_val, N_Sim), 
                  PesaranCCE[[2]][,(5+10)], PesaranCCE[[2]][,(2+2*10)]-rep(c_val, N_Sim),PesaranCCE[[2]][,(5+2*10)],  OracleLSA[[2]][,1]-rep(c_val, N_Sim), OracleLSA[[2]][,2]-rep(c_val, N_Sim),  OracleLSA[[2]][,3]-rep(c_val, N_Sim), OracleLSA[[2]][,5], OracleLSA[[2]][,(2+10)]-rep(c_val, N_Sim), 
                  OracleLSA[[2]][,(5+10)], OracleLSA[[2]][,(2+2*10)]-rep(c_val, N_Sim),OracleLSA[[2]][,(5+2*10)], LSA[[2]][,1]-rep(c_val, N_Sim), LSA[[2]][,2]-rep(c_val, N_Sim), LSA[[2]][,3]-rep(c_val, N_Sim), LSA[[2]][,5], LSA[[2]][,(2+10)]-rep(c_val, N_Sim), LSA[[2]][,(5+10)], LSA[[2]][,(2+2*10)]-rep(c_val, N_Sim), 
                  LSA[[2]][,(5+2*10)], OracleLassoA[[2]][,1]-rep(c_val, N_Sim), OracleLassoA[[2]][,2]-rep(c_val, N_Sim), OracleLassoA[[2]][,3]-rep(c_val, N_Sim), OracleLassoA[[2]][,10], OracleLassoA[[2]][,(2+10)]-rep(c_val, N_Sim), 
                  OracleLassoA[[2]][,(5+10)], OracleLassoA[[2]][,(2+2*10)]-rep(c_val, N_Sim), OracleLassoA[[2]][,(5+2*10)], LassoA[[2]][,1]-rep(c_val, N_Sim), LassoA[[2]][,2]-rep(c_val, N_Sim), LassoA[[2]][,3]-rep(c_val, N_Sim), LassoA[[2]][,5], LassoA[[2]][,(2+10)]-rep(c_val, N_Sim), LassoA[[2]][,(5+10)], 
                   LassoA[[2]][,(2+2*10)]-rep(c_val, N_Sim), LassoA[[2]][,(5+2*10)]),
                
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40), seq(42, 49)),
        col = col_vec_A, cex = 0.2, boxwex = 0.7, lwd = 0.8, whisklty = 1)
title("p =  31",line=0.3, cex.main = 1)
axis(2, las =0, at = c(1, 10, 19, 27, 37, 46), labels = c(TeX(r"(LS-O$^2$)"), "CCE","LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))

abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(h = 41, lwd = 1)
abline(v = 0)


        

## Scenario B
# Boxplot for group representatives for each estimator
boxplot(data.frame(OracleOracleLSB[[2]][,1]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,2]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,3]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,5]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[2]][,8]-rep(c_val, N_Sim), OracleLSB[[2]][,1]-rep(c_val, N_Sim), OracleLSB[[2]][,2]-rep(c_val, N_Sim),  OracleLSB[[2]][,3]-rep(c_val, N_Sim),  OracleLSB[[2]][,5], OracleLSB[[2]][,(2+150)]-rep(c_val, N_Sim),  
                  OracleLSB[[2]][,(5+150)],  OracleLSB[[2]][,(2+2*150)]-rep(c_val, N_Sim), OracleLSB[[2]][,(5+2*150)], LSB[[2]][,1]-rep(c_val, N_Sim), LSB[[2]][,2]-rep(c_val, N_Sim), LSB[[2]][,3]-rep(c_val, N_Sim), LSB[[2]][,5], LSB[[2]][,(2+150)]-rep(c_val, N_Sim), LSB[[2]][,(5+150)], LSB[[2]][,(2+2*150)]-rep(c_val, N_Sim), 
                  LSB[[2]][,(5+2*150)], OracleLassoB[[2]][,1]-rep(c_val, N_Sim), OracleLassoB[[2]][,2]-rep(c_val, N_Sim), OracleLassoB[[2]][,3]-rep(c_val, N_Sim), OracleLassoB[[2]][,5], OracleLassoB[[2]][,(2+150)]-rep(c_val, N_Sim), 
                  OracleLassoB[[2]][,(5+150)], OracleLassoB[[2]][,(2+2*150)]-rep(c_val, N_Sim), OracleLassoB[[2]][,(5+2*150)],  LassoB[[2]][,1]-rep(c_val, N_Sim), LassoB[[2]][,2]-rep(c_val, N_Sim), LassoB[[2]][,3]-rep(c_val, N_Sim), LassoB[[2]][,5], LassoB[[2]][,(2+150)]-rep(c_val, N_Sim), LassoB[[2]][,(5+150)], 
                   LassoB[[2]][,(2+2*150)]-rep(c_val, N_Sim), LassoB[[2]][,(5+2*150)]), 
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40)),
        col = col_vec2, cex = 0.2, boxwex = 0.6, lwd = 0.8, whisklty = 1)
title("p =  451",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19, 28, 37), labels = c(TeX(r"(LS-O$^2$)"), "LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(v = 0)




# p = 3

## Scenario A
# Boxplot for group representatives for each estimator




boxplot(data.frame( 
                  OracleOracleLSA[[3]][,1]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,2]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,3]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSA[[3]][,6]-rep(c_val, N_Sim), PesaranCCE[[3]][,1]-rep(c_val, N_Sim),  PesaranCCE[[3]][,2]-rep(c_val, N_Sim),  PesaranCCE[[3]][,3]-rep(c_val, N_Sim), PesaranCCE[[3]][,5], PesaranCCE[[3]][,(2+15)]-rep(c_val, N_Sim), 
                  PesaranCCE[[3]][,(5+15)], PesaranCCE[[3]][,(2+2*15)]-rep(c_val, N_Sim),PesaranCCE[[3]][,(5+2*15)], OracleLSA[[3]][,1]-rep(c_val, N_Sim), OracleLSA[[3]][,2]-rep(c_val, N_Sim),  OracleLSA[[3]][,3]-rep(c_val, N_Sim), OracleLSA[[3]][,5], OracleLSA[[3]][,(2+15)]-rep(c_val, N_Sim), 
                  OracleLSA[[3]][,(5+15)], OracleLSA[[3]][,(2+2*15)]-rep(c_val, N_Sim),OracleLSA[[3]][,(5+2*15)], LSA[[3]][,1]-rep(c_val, N_Sim), LSA[[3]][,2]-rep(c_val, N_Sim), LSA[[3]][,3]-rep(c_val, N_Sim), LSA[[3]][,5], LSA[[3]][,(2+15)]-rep(c_val, N_Sim), LSA[[3]][,(5+15)], LSA[[3]][,(2+2*15)]-rep(c_val, N_Sim), 
                  LSA[[3]][,(5+2*15)], OracleLassoA[[3]][,1]-rep(c_val, N_Sim), OracleLassoA[[3]][,2]-rep(c_val, N_Sim), OracleLassoA[[3]][,3]-rep(c_val, N_Sim), OracleLassoA[[3]][,15], OracleLassoA[[3]][,(2+15)]-rep(c_val, N_Sim), OracleLassoA[[3]][,(5+15)], OracleLassoA[[3]][,(2+2*15)]-rep(c_val, N_Sim), OracleLassoA[[3]][,(5+2*15)], LassoA[[3]][,1]-rep(c_val, N_Sim), LassoA[[3]][,2]-rep(c_val, N_Sim), LassoA[[3]][,3]-rep(c_val, N_Sim), LassoA[[3]][,5], LassoA[[3]][,(2+15)]-rep(c_val, N_Sim), LassoA[[3]][,(5+15)], 
                   LassoA[[3]][,(2+2*15)]-rep(c_val, N_Sim), LassoA[[3]][,(5+2*15)]),
                 
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40), seq(42, 49)),
        col = col_vec_A, cex = 0.2, boxwex = 0.7, lwd = 0.8, whisklty = 1)
title("p =  46",line=0.3, cex.main = 1)
axis(2, las =0, at = c(1, 10, 19, 27, 37, 46), labels = c(TeX(r"(LS-O$^2$)"), "CCE","LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))

abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(h = 41, lwd = 1)
abline(v = 0)
        

## Scenario B
# Boxplot for group representatives for each estimator
boxplot(data.frame( OracleOracleLSB[[3]][,1]-rep(c_val, N_Sim), OracleOracleLSB[[3]][,2]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[3]][,3]-rep(c_val, N_Sim), OracleOracleLSB[[3]][,5]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[3]][,10]-rep(c_val, N_Sim), OracleLSB[[3]][,1]-rep(c_val, N_Sim), OracleLSB[[3]][,2]-rep(c_val, N_Sim),  
                  OracleLSB[[3]][,3]-rep(c_val, N_Sim), OracleLSB[[3]][,5], 
                  OracleLSB[[3]][,(2+300)]-rep(c_val,N_Sim),  
                  OracleLSB[[3]][,(5+300)], OracleLSB[[3]][,(2+2*300)]-rep(c_val, N_Sim), OracleLSB[[3]][,(5+2*300)], LSB[[3]][,1]-rep(c_val, N_Sim), LSB[[3]][,2]-rep(c_val, N_Sim), LSB[[3]][,3]-rep(c_val, N_Sim), 
                  LSB[[3]][,5], LSB[[3]][,(2+300)]-rep(c_val, N_Sim), LSB[[3]][,(5+300)], 
                  LSB[[3]][,(2+2*300)]-rep(c_val, N_Sim), 
                  LSB[[3]][,(5+2*300)], 
                  OracleLassoB[[3]][,1]-rep(c_val, N_Sim), OracleLassoB[[3]][,2]-rep(c_val, N_Sim), 
                  OracleLassoB[[3]][,3]-rep(c_val, N_Sim), OracleLassoB[[3]][,5], 
                  OracleLassoB[[3]][,(2+300)]-rep(c_val, N_Sim), OracleLassoB[[3]][,(5+300)], 
                  OracleLassoB[[3]][,(2+2*300)]-rep(c_val, N_Sim), OracleLassoB[[3]][,(5+2*300)],  LassoB[[3]][,1]-rep(c_val, N_Sim), LassoB[[3]][,2]-rep(c_val, N_Sim), LassoB[[3]][,3]-rep(c_val, N_Sim), 
                   LassoB[[3]][,5], LassoB[[3]][,(2+300)]-rep(c_val, N_Sim), LassoB[[3]][,(5+300)], 
                   LassoB[[3]][,(2+2*300)]-rep(c_val, N_Sim), LassoB[[3]][,(5+2*300)]), 
                  
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40)),
        col = col_vec2, cex = 0.2, boxwex = 0.6, lwd = 0.8, whisklty = 1)
title("p =  901",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19, 28, 37), labels = c(TeX(r"(LS-O$^2$)"), "LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(v = 0)
```













## Collect inference results

```{r}
signal <- 1 # Signal 1,2,3 correspond to c** = 0, 0.01, 0.02
gamma <- 1
rejA <- numeric(3)
rejB <- numeric(3)
rejC <- 0

rej <- matrix(NA, nrow = 7, ncol = 3)


count <- 1
for (alpha in c(0.01, 0.05, 0.1)) {
  
z_alpha <- qnorm(1-alpha/2)
    
  for (p in 1:3) {
  
  tmpA <- 0
  tmpB <- 0
  tmpC <- 0
  
  for (sim in 1:N_Sim) {
    
    tmpA <- tmpA + as.numeric(abs(results_Factors[[sim]][[gamma]][[p]][[1]][["TestStatistic"]][signal]) > 
                                z_alpha)
    tmpB <- tmpB + as.numeric(abs(results_Factors[[sim]][[gamma]][[p]][[2]][["TestStatistic"]][signal]) > 
                                z_alpha)
    if(p == 3){
    tmpC <- tmpC + as.numeric(abs(results_Factors[[sim]][[gamma]][[p]][[3]][["TestStatistic"]][signal]) > 
                                z_alpha)
    }
   
  }
  
  rejA[p] <- tmpA
  rejB[p] <- tmpB
  if(p == 3){
    rejC <- tmpC
  }
  }
  tmp <- c(rejA, rejB, rejC)/N_Sim

  rej[, count] <- tmp

  count <- count + 1
}
```











## Robustness check (KHat = 6)


```{r}
# Collect HighK results and compare with oracle results

gamma <- 1
T_dim <- 50

  LassoA <-  vector(mode = 'list', length = 3)
  OracleLassoA <-  vector(mode = 'list', length = 3)
  LSA <- vector(mode = 'list', length = 3)
  OracleLSA <- vector(mode = 'list', length = 3)
  OracleOracleLSA <-  vector(mode = 'list', length = 3)
  PesaranCCE <-  vector(mode = 'list', length = 3)

  LassoB <-  vector(mode = 'list', length = 3)
  OracleLassoB <- vector(mode = 'list', length = 3)
  LSB <-  vector(mode = 'list', length = 3)
  OracleLSB <-  vector(mode = 'list', length = 3)
  OracleOracleLSB <-  vector(mode = 'list', length = 3)


  LassoC <-  vector(mode = 'list', length = 3)
  OracleLassoC <- vector(mode = 'list', length = 3)
  OracleOracleLSC <-  vector(mode = 'list', length = 3)

  
      tmpLassoA <- numeric(pA_vec[2])
      tmpOracleLassoA <- numeric(pA_vec[2])
      tmpLSA <- numeric(pA_vec[2])
      tmpOracleLSA <- numeric(pA_vec[2])
      tmpOracleOracleLSA <- numeric(10)
      tmpPesaranCCE <- numeric(pA_vec[2])

      tmpLassoB <- numeric(pB_vec[2])
      tmpOracleLassoB <- numeric(pB_vec[2])
      tmpLSB <- numeric(pB_vec[2])
      tmpOracleLSB<- numeric(pB_vec[2])
      tmpOracleOracleLSB <- numeric(10)
      
    
      tmpLassoC <- numeric(pC)
      tmpOracleLassoC <- numeric(pC)
      tmpOracleOracleLSC <- numeric(10)
    

    for (sim in 1:N_Sim) {
      tmpLassoA <- rbind(tmpLassoA, results_Factors[[sim]][[gamma]][[2]][[1]]$HighKLasso)
      tmpOracleLassoA <- rbind(tmpOracleLassoA, results_Factors[[sim]][[gamma]][[2]][[1]][["OracleLasso"]])
      tmpLSA<-rbind(tmpLSA, results_Factors[[sim]][[gamma]][[2]][[1]]$HighKLS)
      tmpOracleLSA <- rbind(tmpOracleLSA, results_Factors[[sim]][[gamma]][[2]][[1]][["OracleLS"]])
      tmpOracleOracleLSA<- rbind(tmpOracleOracleLSA, results_Factors[[sim]][[gamma]][[2]][[1]][["OracleOracleLS"]])
      tmpPesaranCCE <- rbind(tmpPesaranCCE, results_Factors[[sim]][[gamma]][[2]][[1]][["PesaranCCE"]])

      tmpLassoB <- rbind(tmpLassoB, results_Factors[[sim]][[gamma]][[2]][[2]]$HighKLasso)
      tmpOracleLassoB <- rbind(tmpOracleLassoB, results_Factors[[sim]][[gamma]][[2]][[2]][["OracleLasso"]])
      tmpLSB <- rbind(tmpLSB, results_Factors[[sim]][[gamma]][[2]][[2]]$HighKLS)
      tmpOracleLSB<- rbind(tmpOracleLSB,  results_Factors[[sim]][[gamma]][[2]][[2]][["OracleLS"]])
      tmpOracleOracleLSB <- rbind(tmpOracleOracleLSB, results_Factors[[sim]][[gamma]][[2]][[2]][["OracleOracleLS"]])

      tmpLassoC <- rbind(tmpLassoC, results_Factors[[sim]][[gamma]][[2]][[3]]$HighKLasso)
      tmpOracleLassoC <- rbind(tmpOracleLassoC,results_Factors[[sim]][[gamma]][[2]][[3]][["OracleLasso"]])
      tmpOracleOracleLSC <- rbind(tmpOracleOracleLSC, results_Factors[[sim]][[gamma]][[2]][[3]][["OracleOracleLS"]])

    }
    LassoA[[3]] <-  tmpLassoA[-1,]
    OracleLassoA[[3]] <- tmpOracleLassoA[-1,]
    LSA[[3]] <- tmpLSA[-1,]
    OracleLSA[[3]] <- tmpOracleLSA[-1,]
    OracleOracleLSA[[3]] <- tmpOracleOracleLSA[-1,]
    PesaranCCE[[3]] <- tmpPesaranCCE[-1,]

    LassoB[[2]] <- tmpLassoB[-1,]
    OracleLassoB[[2]] <- tmpOracleLassoB[-1,]
    LSB[[2]] <- tmpLSB[-1,]
    OracleLSB[[2]] <- tmpOracleLSB[-1,]
    OracleOracleLSB[[2]] <- tmpOracleOracleLSB[-1,]

    LassoC[[3]] <- tmpLassoC[-1,]
    OracleLassoC[[3]] <- tmpOracleLassoC[-1,]
    OracleOracleLSC[[3]] <- tmpOracleOracleLSC[-1,]
```





```{r}
##################### Boxplots for T = 15 and KHat = 6 ############################

# Boxplot for group representatives for each estimator
col_vec2 <- c("green", "blue", "red", "magenta", "bisque", rep(c("green", "blue", "red", "yellow", "magenta", "cyan", "bisque", "darkorange"), 4))
col_vec_A <-  c("green", "blue", "red", "magenta", "bisque", rep(c("green", "blue", "red", "yellow", "magenta", "cyan", "bisque", "darkorange"), 5))


## Scenario C
boxplot(data.frame(OracleOracleLSC[[3]][,1]-rep(c_val, N_Sim), OracleOracleLSC[[3]][,2]-rep(c_val, N_Sim), OracleOracleLSC[[3]][,3]-rep(c_val, N_Sim), 
                  OracleOracleLSC[[3]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSC[[3]][,6]-rep(c_val, N_Sim), OracleLassoC[[3]][,1]-rep(c_val, N_Sim), OracleLassoC[[3]][,2]-rep(c_val, N_Sim), OracleLassoC[[3]][,3]-rep(c_val, N_Sim), OracleLassoC[[3]][,5], 
                  OracleLassoC[[3]][,(2+300)]-rep(c_val, N_Sim), 
                  OracleLassoC[[3]][,(5+300)], OracleLassoC[[3]][,(2+2*300)]-rep(c_val, N_Sim), OracleLassoC[[3]][,(5+2*300)], 
                  LassoC[[3]][,1]-rep(c_val, N_Sim), LassoC[[3]][,2]-rep(c_val, N_Sim), LassoC[[3]][,3]-rep(c_val, N_Sim), LassoC[[3]][,5], LassoC[[3]][,(2+300)]-rep(c_val, N_Sim), 
                   LassoC[[3]][,(5+300)], LassoC[[3]][,(2+2*300)]-rep(c_val, N_Sim), LassoC[[3]][,(5+2*300)]),
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22)), col = col_vec2, cex = 0.2, boxwex = 0.4, lwd = 0.8, whisklty = 1)
title("p =  901",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19), labels = c(TeX(r"(LS-O$^2$)"), "L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(v = 0)




## Scenario A
# Boxplot for group representatives for each estimator




boxplot(data.frame( 
                  OracleOracleLSA[[3]][,1]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,2]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,3]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSA[[3]][,6]-rep(c_val, N_Sim), PesaranCCE[[3]][,1]-rep(c_val, N_Sim),  PesaranCCE[[3]][,2]-rep(c_val, N_Sim),  PesaranCCE[[3]][,3]-rep(c_val, N_Sim), PesaranCCE[[3]][,5], PesaranCCE[[3]][,6]-rep(c_val, N_Sim), 
                  PesaranCCE[[3]][,9], PesaranCCE[[3]][,10]-rep(c_val, N_Sim), PesaranCCE[[3]][,13], OracleLSA[[3]][,1]-rep(c_val, N_Sim), OracleLSA[[3]][,2]-rep(c_val, N_Sim),  OracleLSA[[3]][,3]-rep(c_val, N_Sim), OracleLSA[[3]][,5], OracleLSA[[3]][,6]-rep(c_val, N_Sim), 
                  OracleLSA[[3]][,9], OracleLSA[[3]][,10]-rep(c_val, N_Sim),OracleLSA[[3]][,13], LSA[[3]][,1]-rep(c_val, N_Sim), LSA[[3]][,2]-rep(c_val, N_Sim), LSA[[3]][,3]-rep(c_val, N_Sim), LSA[[3]][,5], LSA[[3]][,6]-rep(c_val, N_Sim), LSA[[3]][,9], LSA[[3]][,10]-rep(c_val, N_Sim), 
                  LSA[[3]][,13], OracleLassoA[[3]][,1]-rep(c_val, N_Sim), OracleLassoA[[3]][,2]-rep(c_val, N_Sim), OracleLassoA[[3]][,3]-rep(c_val, N_Sim), OracleLassoA[[3]][,5], OracleLassoA[[3]][,6]-rep(c_val, N_Sim), OracleLassoA[[3]][,9], OracleLassoA[[3]][,10]-rep(c_val, N_Sim), OracleLassoA[[3]][,13], LassoA[[3]][,1]-rep(c_val, N_Sim), LassoA[[3]][,2]-rep(c_val, N_Sim), LassoA[[3]][,3]-rep(c_val, N_Sim), LassoA[[3]][,5], LassoA[[3]][,6]-rep(c_val, N_Sim), LassoA[[3]][,9], 
                   LassoA[[3]][,10]-rep(c_val, N_Sim), LassoA[[3]][,13]),
                 
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40), seq(42, 49)),
        col = col_vec_A, cex = 0.2, boxwex = 0.7, lwd = 0.8, whisklty = 1)
title("p =  13",line=0.3, cex.main = 1)
axis(2, las =0, at = c(1, 10, 19, 27, 37, 46), labels = c(TeX(r"(LS-O$^2$)"), "CCE","LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))

abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(h = 41, lwd = 1)
abline(v = 0)
        

## Scenario B
# Boxplot for group representatives for each estimator
boxplot(data.frame( OracleOracleLSB[[2]][,1]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,2]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[2]][,3]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,5]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[2]][,10]-rep(c_val, N_Sim), OracleLSB[[2]][,1]-rep(c_val, N_Sim), OracleLSB[[2]][,2]-rep(c_val, N_Sim),  
                  OracleLSB[[2]][,3]-rep(c_val, N_Sim), OracleLSB[[2]][,5], 
                  OracleLSB[[2]][,(2+50)]-rep(c_val,N_Sim),  
                  OracleLSB[[2]][,(5+50)], OracleLSB[[2]][,(2+2*50)]-rep(c_val, N_Sim), OracleLSB[[2]][,(5+2*50)], LSB[[2]][,1]-rep(c_val, N_Sim), LSB[[2]][,2]-rep(c_val, N_Sim), LSB[[2]][,3]-rep(c_val, N_Sim), 
                  LSB[[2]][,5], LSB[[2]][,(2+50)]-rep(c_val, N_Sim), LSB[[2]][,(5+50)], 
                  LSB[[2]][,(2+2*50)]-rep(c_val, N_Sim), 
                  LSB[[2]][,(5+2*50)], 
                  OracleLassoB[[2]][,1]-rep(c_val, N_Sim), OracleLassoB[[2]][,2]-rep(c_val, N_Sim), 
                  OracleLassoB[[2]][,3]-rep(c_val, N_Sim), OracleLassoB[[2]][,5], 
                  OracleLassoB[[2]][,(2+50)]-rep(c_val, N_Sim), OracleLassoB[[2]][,(5+50)], 
                  OracleLassoB[[2]][,(2+2*50)]-rep(c_val, N_Sim), OracleLassoB[[2]][,(5+2*50)],  LassoB[[2]][,1]-rep(c_val, N_Sim), LassoB[[2]][,2]-rep(c_val, N_Sim), LassoB[[2]][,3]-rep(c_val, N_Sim), 
                   LassoB[[2]][,5], LassoB[[2]][,(2+50)]-rep(c_val, N_Sim), LassoB[[2]][,(5+50)], 
                   LassoB[[2]][,(2+2*50)]-rep(c_val, N_Sim), LassoB[[2]][,(5+2*50)]), 
                  
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40)),
        col = col_vec2, cex = 0.2, boxwex = 0.6, lwd = 0.8, whisklty = 1)
title( "p = 151" , line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19, 28, 37), labels = c(TeX(r"(LS-O$^2$)"), "LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(v = 0)
```











```{r}

################ Boxplots for T = 50 AND K = 6 ###########################
col_vec2 <- c("green", "blue", "red", "magenta", "bisque", rep(c("green", "blue", "red", "yellow", "magenta", "cyan", "bisque", "darkorange"), 4))
col_vec_A <-  c("green", "blue", "red", "magenta", "bisque", rep(c("green", "blue", "red", "yellow", "magenta", "cyan", "bisque", "darkorange"), 5))


## Scenario A
# Boxplot for group representatives for each estimator

boxplot(data.frame( 
                  OracleOracleLSA[[3]][,1]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,2]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,3]-rep(c_val, N_Sim), OracleOracleLSA[[3]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSA[[3]][,6]-rep(c_val, N_Sim), PesaranCCE[[3]][,1]-rep(c_val, N_Sim),  PesaranCCE[[3]][,2]-rep(c_val, N_Sim),  PesaranCCE[[3]][,3]-rep(c_val, N_Sim), PesaranCCE[[3]][,5], PesaranCCE[[3]][,(2+15)]-rep(c_val, N_Sim), 
                  PesaranCCE[[3]][,(5+15)], PesaranCCE[[3]][,(2+2*15)]-rep(c_val, N_Sim),PesaranCCE[[3]][,(5+2*15)], OracleLSA[[3]][,1]-rep(c_val, N_Sim), OracleLSA[[3]][,2]-rep(c_val, N_Sim),  OracleLSA[[3]][,3]-rep(c_val, N_Sim), OracleLSA[[3]][,5], OracleLSA[[3]][,(2+15)]-rep(c_val, N_Sim), 
                  OracleLSA[[3]][,(5+15)], OracleLSA[[3]][,(2+2*15)]-rep(c_val, N_Sim),OracleLSA[[3]][,(5+2*15)], LSA[[3]][,1]-rep(c_val, N_Sim), LSA[[3]][,2]-rep(c_val, N_Sim), LSA[[3]][,3]-rep(c_val, N_Sim), LSA[[3]][,5], LSA[[3]][,(2+15)]-rep(c_val, N_Sim), LSA[[3]][,(5+15)], LSA[[3]][,(2+2*15)]-rep(c_val, N_Sim), 
                  LSA[[3]][,(5+2*15)], OracleLassoA[[3]][,1]-rep(c_val, N_Sim), OracleLassoA[[3]][,2]-rep(c_val, N_Sim), OracleLassoA[[3]][,3]-rep(c_val, N_Sim), OracleLassoA[[3]][,15], OracleLassoA[[3]][,(2+15)]-rep(c_val, N_Sim), OracleLassoA[[3]][,(5+15)], OracleLassoA[[3]][,(2+2*15)]-rep(c_val, N_Sim), OracleLassoA[[3]][,(5+2*15)], LassoA[[3]][,1]-rep(c_val, N_Sim), LassoA[[3]][,2]-rep(c_val, N_Sim), LassoA[[3]][,3]-rep(c_val, N_Sim), LassoA[[3]][,5], LassoA[[3]][,(2+15)]-rep(c_val, N_Sim), LassoA[[3]][,(5+15)], 
                   LassoA[[3]][,(2+2*15)]-rep(c_val, N_Sim), LassoA[[3]][,(5+2*15)]),
                 
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40), seq(42, 49)),
        col = col_vec_A, cex = 0.2, boxwex = 0.7, lwd = 0.8, whisklty = 1)
title("p =  46",line=0.3, cex.main = 1)
axis(2, las =0, at = c(1, 10, 19, 27, 37, 46), labels = c(TeX(r"(LS-O$^2$)"), "CCE","LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))

abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(h = 41, lwd = 1)
abline(v = 0)
        

## Scenario B
# Boxplot for group representatives for each estimator
boxplot(data.frame( OracleOracleLSB[[2]][,1]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,2]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[2]][,3]-rep(c_val, N_Sim), OracleOracleLSB[[2]][,5]-rep(c_val, N_Sim), 
                  OracleOracleLSB[[2]][,10]-rep(c_val, N_Sim), OracleLSB[[2]][,1]-rep(c_val, N_Sim), OracleLSB[[2]][,2]-rep(c_val, N_Sim),  
                  OracleLSB[[2]][,3]-rep(c_val, N_Sim), OracleLSB[[2]][,5], 
                  OracleLSB[[2]][,(2+150)]-rep(c_val,N_Sim),  
                  OracleLSB[[2]][,(5+150)], OracleLSB[[2]][,(2+2*150)]-rep(c_val, N_Sim), OracleLSB[[2]][,(5+2*150)], LSB[[2]][,1]-rep(c_val, N_Sim), LSB[[2]][,2]-rep(c_val, N_Sim), LSB[[2]][,3]-rep(c_val, N_Sim), 
                  LSB[[2]][,5], LSB[[2]][,(2+150)]-rep(c_val, N_Sim), LSB[[2]][,(5+150)], 
                  LSB[[2]][,(2+2*150)]-rep(c_val, N_Sim), 
                  LSB[[2]][,(5+2*150)], 
                  OracleLassoB[[2]][,1]-rep(c_val, N_Sim), OracleLassoB[[2]][,2]-rep(c_val, N_Sim), 
                  OracleLassoB[[2]][,3]-rep(c_val, N_Sim), OracleLassoB[[2]][,5], 
                  OracleLassoB[[2]][,(2+150)]-rep(c_val, N_Sim), OracleLassoB[[2]][,(5+150)], 
                  OracleLassoB[[2]][,(2+2*150)]-rep(c_val, N_Sim), OracleLassoB[[2]][,(5+2*150)],  LassoB[[2]][,1]-rep(c_val, N_Sim), LassoB[[2]][,2]-rep(c_val, N_Sim), LassoB[[2]][,3]-rep(c_val, N_Sim), 
                   LassoB[[2]][,5], LassoB[[2]][,(2+150)]-rep(c_val, N_Sim), LassoB[[2]][,(5+150)], 
                   LassoB[[2]][,(2+2*150)]-rep(c_val, N_Sim), LassoB[[2]][,(5+2*150)]), 
                  
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22), seq(24,31), seq(33,40)),
        col = col_vec2, cex = 0.2, boxwex = 0.6, lwd = 0.8, whisklty = 1)
title("p =  451",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19, 28, 37), labels = c(TeX(r"(LS-O$^2$)"), "LS-O", "LS","L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(h = 23, lwd = 1)
abline(h = 32, lwd = 1)
abline(v = 0)





## Scenario C
boxplot(data.frame(OracleOracleLSC[[3]][,1]-rep(c_val, N_Sim), OracleOracleLSC[[3]][,2]-rep(c_val, N_Sim), OracleOracleLSC[[3]][,3]-rep(c_val, N_Sim), 
                  OracleOracleLSC[[3]][,4]-rep(c_val, N_Sim), 
                  OracleOracleLSC[[3]][,6]-rep(c_val, N_Sim), OracleLassoC[[3]][,1]-rep(c_val, N_Sim), OracleLassoC[[3]][,2]-rep(c_val, N_Sim), OracleLassoC[[3]][,3]-rep(c_val, N_Sim), OracleLassoC[[3]][,5], 
                  OracleLassoC[[3]][,(2+1000)]-rep(c_val, N_Sim), 
                  OracleLassoC[[3]][,(5+1000)], OracleLassoC[[3]][,(2+2*1000)]-rep(c_val, N_Sim), OracleLassoC[[3]][,(5+2*1000)], 
                  LassoC[[3]][,1]-rep(c_val, N_Sim), LassoC[[3]][,2]-rep(c_val, N_Sim), LassoC[[3]][,3]-rep(c_val, N_Sim), LassoC[[3]][,5], LassoC[[3]][,(2+1000)]-rep(c_val, N_Sim), 
                   LassoC[[3]][,(5+1000)], LassoC[[3]][,(2+2*1000)]-rep(c_val, N_Sim), LassoC[[3]][,(5+2*1000)]),
        yaxt = "n",  horizontal = TRUE, at = c(seq(0,4), seq(6,13), seq(15,22)), col = col_vec2, cex = 0.2, boxwex = 0.4, lwd = 0.8, whisklty = 1)
title("p =  3001",line=0.3, cex.main = 1)
axis(2, las = 0, at = c(2, 10, 19), labels = c(TeX(r"(LS-O$^2$)"), "L-O", "L") , tick = FALSE, cex.axis = 0.8, mgp = c(3, 0.25, 1))
abline(h = 5, lwd = 1)
abline(h = 14, lwd = 1)
abline(v = 0)
```
















